### 2025-06-13 manuscripts/10-JERP-v3/manuscript_title_etc.tex
edit manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 4. Define Thanks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ACKNOWLEDGMENTS}{
I thank Patrick Button, Willa Friedman, Chinhui Juhn, Vikram Maheshri, and Yona Rubinstein for their support and advice. I also thank Aimee Chin, Steven Craig, German Cubas, Elaine Liu, Fan Wang, and the participants of the Applied Microeconomics Workshop at the University of Houston, and European Society for Population Economics (ESPE) for helpful feedback.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
% Do individuals with ethnically Hispanic names face labor market discrimination? In this study, I analyze the impact of Hispanic-sounding surnames on wages, considering inter-ethnic children and the distinct traits of native and Hispanic surnames. I examine the earnings of individuals with one White and one Hispanic parent, finding that those with Hispanic surnames often experience wage disparities. My findings reveal a notable wage gap favoring individuals with White surnames. Although males born to Hispanic fathers and White mothers earn 5 percentage points less than those born to White fathers and Hispanic mothers, this difference can be attributed to educational variances. However, this shouldn't imply an absence of discrimination; it may reflect discrimination in human capital accumulation. Furthermore, I investigate the impact of self-identifying as Hispanic on earnings. Men with a Spanish-sounding last name who identify as Hispanic earn notably less than those who do not, largely due to educational differences.

Do individuals with Hispanic surnames face labor market discrimination? This study analyzes the impact of likely Hispanic surnames on wages among Americans with one White and one Hispanic parent. I find that individuals that likely have Hispanic surnames (i.e., those with a Hispanic father) often earn less, with a notable wage gap favoring those with White-sounding surnames. People born to Hispanic fathers and White mothers receive 0.2 fewer years of education than those born to White fathers and Hispanic mothers. Men born to Hispanic fathers and White mothers are 1 percentage point more likely to be unemployed, and they earn 5 percentage points less than those born to White fathers and Hispanic mothers. I also show that this gap can largely be explained by educational differences.  \PAPERJEL}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 4. Define Thanks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ACKNOWLEDGMENTS}{
I thank Patrick Button, Willa Friedman, Chinhui Juhn, Vikram Maheshri, and Yona Rubinstein for their support and advice. I also thank Aimee Chin, Steven Craig, German Cubas, Elaine Liu, Fan Wang, and the participants of the Applied Microeconomics Workshop at the University of Houston, the European Society for Population Economics (ESPE), the anonymous referees, and the editors for helpful feedback.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{

Do individuals with Hispanic surnames face discrimination in access to education and the labor market? This study analyzes the impact of likely Hispanic surnames on wages among Americans with one White and one Hispanic parent. Individuals who likely have Hispanic surnames (i.e. those with a Hispanic father) often complete less education and earn less, with a notable wage gap favoring those with white-sounding surnames. People born to Hispanic fathers and White mothers receive 0.2 fewer years of education than those born to White fathers and Hispanic mothers. Men born to Hispanic fathers and White mothers earn 5 percentage points less than those born to White fathers and Hispanic mothers, and they are 1 percentage point more likely to be unemployed. I also show that this gap can be largely explained by educational differences.  \PAPERJEL}

### 2025-06-13 manuscripts/10-JERP-v3/submit_journal-main.tex
start working on R&R v2
edit manuscript

\subsection*{Data Availability Statement}
The data that support the findings of this study will be openly available to all researchers after the review process. For immediate information regarding the data and/or computer programs used for this study, please contact Hussain Hadah at hhadah@tulane.edu.

@@

\subsection*{Conflict of Interest Disclosure}
The author declares that they have no conflicts of interest regarding the publication of this manuscript.

@@

    \section{Responses to Referee One}
        I would like to thank referee one for the insightful comments and suggestions. Below is a detailed response to the comments and suggestions.
    \begin{spacing}{\rrquote}
    \begin{quotation}
    \textbf{R1: } 1. My first concern relates to the threats to identification. It is feasible that children born to HW couples may differ systematically to children born to WH couples, particularly with respect to unobservable characteristics important for labor market outcomes. For example, HW pairs may exhibit differing parental characteristics related to parenting styles, parental preferences for education, gender norms and beliefs. The paper would be improved by including an expanded discussion around the threat to identification. In light of these issues, the paper would be improved by providing a more thorough discussion of the relative advantages of the current approach, compared to the conventional Oaxaca-Blinder decomposition.
    \end{quotation}
    \end{spacing}

    \begin{spacing}{\rrxspc}
        I included an extensive discussion of the differences between HW and WH couples. These differences, that includes cultural differences, in couple of sections throughout the manuscript. While I acknowledge the concern, the estimation strategy rest of the fact that selection in the marriage market decreases the differences between HW and WH couples. This is the reason why comparing children of intermarried couples provides a better comparison than comparing children of endogamous marriages, i.e. marriages where both parents are either non-Hispanic White or Hispanic. I also included a discussion of the relative advantages of the current approach compared to the conventional Oaxaca-Blinder-Kitagawa decomposition. I argue that the current approach provides a more accurate estimate of gaps that are due to discrimination. In fact, the concern the reviewer raises is one of the reasons why my approach is preferred over the Oaxaca-Blinder-Kitagawa since children of endogamous marriages are more likely to have different characteristics than children of intermarried couples, including those that are unobservable. I argue, and show from the data, that children of intermarried couples are more likely to have similar characteristics than children of endogamous couples, see sections 3.1, and 4.
    \end{spacing}

    \begin{spacing}{\rrxspc}
    \begin{quotation}
        \textbf{R1: } 2. The analysis sample is restricted to individuals who self-identify as ‘White’. It is likely that this self-identification of ethnicity is endogenous to labor market outcomes. Importantly, the unobservable determinants of racial identification are potentially correlated with labor market outcomes. The paper would be improved by including a more thorough discussion of this (sample) selection issue. Related to this is the depiction of parents born in the United States as ’White’. This seems particularly over-simplifying and ignores the long history of immigration. A more accurate description would be to refer to this group as US born.
        \end{quotation}
        \end{spacing}

    \begin{spacing}{\rrxspc}
        I thank the reviewer for this comment and concern over the endogeneity of self-identification and labor market outcomes. I added some discussion over why I chose those who self-identify as White. I argue that inclusion those that are not White could contaminate the estimate of bias against Hispanics due to the racial signal. Moreover, \autocite{hadah2024effect} shows that there exists strong correlation between bias against Hispanics and self-reported Hispanic identity. Their results show that by not including Hispanics that attrit in the estimation of racial and ethnic gaps, the estimate of bias against Hispanics could be overestimated in the most biased states---more on ethnic attrition of Hispanics could be found in \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}. Regarding the comment of oversimplifying and ignoring the long history of immigration in the US, the majority of immigrants from Spanish-speaking countries in the US are first- and second-generation (see \autocite{antman2020ethnic}). I also show that the probability that parents are second-generation+ immigrants from Spanish-speaking countries is very low using Census data from 1960 to 2000, see Table 5. 
    \end{spacing}

    \begin{spacing}{\rrxspc}
        \begin{quotation}
            \textbf{R1: } 3. The discussion on the construction of the ‘synthetic parents’ is somewhat brief. The paper suggests that the potential parents are matched using the birth year of the child and the parent’s place of birth to the children’s information collected in the CPS sample. While not explicitly stated in the paper, I assume that this sample of synthetic parents is used to construct mean parental education and family income at the time of the birth of the child. The process for matching the potential parents to the children is somewhat aggregated and their is likely considerable heterogeneity in the mean educational attainment of the potential parents within the set of children with the same birth year with the same parent’s country of birth. The paper could be improved by exploring the possibility of improving the quality of the match of potential parents by including further characteristics to match the potential parents to their children.
    \end{quotation}
        \end{spacing}

    \begin{spacing}{\rrxspc}
            I appreciate this insightful suggestion. I have expanded the discussion and provided a detailed example of the 'synthetic parents' construction methodology. While additional matching dimensions would be valuable, the limitations of publicly available data constrain the potential matching criteria. Nevertheless, the current approach provides meaningful estimates while acknowledging these data constraints.
    \end{spacing}

    \begin{spacing}{\rrxspc}
        \begin{quotation}
            \textbf{R1: } 4. The description of the estimated model is somewhat brief. However, there are two main issues associated with statistical inference on the estimated parameters in model (1). First, there is a ‘generated regressor’ issue associated with using estimated group-level parental education. A failure to account for this sampling variation will lead to misleadingly small standard errors. Second, given this group structure for parental education, it seems reasonable to assume that the model errors are uncorrelated across clusters but correlated within (potential parents) clusters. It is well understood that failing to account for this ‘clustering’ problem can lead to misleadingly small standard errors, narrow confidence intervals, and low p-values.
        \end{quotation}
    \end{spacing}

    \begin{spacing}{\rrxspc}
        Thank you for these important methodological points. Regarding the generated regressor issue: The parental characteristics are included solely as controls and not for inference purposes. I do not interpret these coefficients, as my primary interest lies in $\beta_1$, which captures the gap between Hispanic and White last names. Since I am only using these synthetic characteristics as controls and not making inference about their coefficients, this should not affect the standard errors or p-values of my coefficient of interest $\beta_1$, which is not a generated regressor.
    \end{spacing}

    \begin{spacing}{\rrxspc}
        \begin{quotation}
            \textbf{R1: } 5. The paper would be improved through an expanded discussion of the impact of measurement error on the reported estimates. While there is a well understood result in the measurement error literature that measures of group mean parental education will provide estimates that are more robust to the presence of measurement error in individual level measures of parental education, there is still an issue with the non-random attrition of potential parents. Specifically, not all potential parents have children in the CPS sample, nor do all children in the CPS sample have parents in the sample of potential parents. Moreover, the non-random attrition of potential parents implies that mean parental education may be systematically higher or lower than the actual parental education of the children in the CPS sample. The paper would be improved by providing an expanded discussion of the likely impacts of measurement error on the reported estimates.
        \end{quotation}
    \end{spacing}

    \begin{spacing}{\rrxspc}
        Thank you for these important methodological points. Let me clarify that the synthetic parents are constructed using the birth year of the child. The place of birth of parents---mothers and fathers---are questions that are asked of all participants in the Current Population Survey (CPS) starting 1994. Therefore, I do not use the information of parents that are in the CPS sample at the time of the survey. Thus, the concern over the attrition of parents in the sample is not applicable to my analysis. Please see the data section for a discussion of the data used in the analysis.
    \end{spacing}
    \clearpage
    \pagebreak

@@

\clearpage
\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PART VII. Online Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{refsection}
% Reset section numbering
\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thesubsection}{\Alph{section}.\arabic{subsection}}
\renewcommand{\thesubsubsection}{\Alph{section}.\arabic{subsection}.\arabic{subsubsection}}

>>>>

\subsection*{Data Availability Statement}
The data that support the findings of this study will be openly available to all researchers after the review process. For immediate information on the data and / or computer programs used for this study, please contact Hussain Hadah at hhadah@tulane.edu.

@@

\subsection*{Conflict of Interest Disclosure}
The author declares that they have no conflict of interest with respect to the publication of this manuscript.

@@

\section{Responses to Referee One}
I would like to thank referee one for the insightful comments and suggestions. Below is a detailed response to the comments and suggestions.
\begin{spacing}{\rrquote}
\begin{quotation}
\textbf{R1: } 1. My first concern relates to the threats to identification. It is feasible that children born to HW couples may differ systematically to children born to WH couples, particularly with respect to unobservable characteristics important for labor market outcomes. For example, HW pairs may exhibit differing parental characteristics related to parenting styles, parental preferences for education, gender norms and beliefs. The paper would be improved by including an expanded discussion around the threat to identification. In light of these issues, the paper would be improved by providing a more thorough discussion of the relative advantages of the current approach, compared to the conventional Oaxaca-Blinder decomposition.
\end{quotation}
\end{spacing}
\begin{spacing}{\rrxspc}
    Thank you for raising these concerns. I have significantly expanded the discussion of identification threats and the advantages of my approach compared to traditional methods. In Section \ref{sec:hw-wh-couples-data} (``From the Data: The Differences Between HW and WH Couples''), I now explicitly acknowledge that ``Unlike traditional decomposition methods, this comparison directly isolates the role of surname signaling, reducing the confounding effect of background disparities. By focusing specifically on children from interethnic marriages with similar parental characteristics but different surname ethnicities, I use a more targeted comparison group that better isolates the effect of perceived ethnicity from family background. Traditional decomposition approaches would struggle to separate discrimination effects from the broader socioeconomic gaps between Hispanic and White families overall. The smaller educational and income disparities between HW and WH families compared to HH and WW families, allowing for a clearer attribution of outcome differences to discrimination rather than unobserved heterogeneity. Nevertheless, I acknowledge that residual selection bias remains a concern, particularly regarding cultural and attitudinal factors that may systematically differ between HW and WH households despite similar educational and economic outcomes.''
\end{spacing}

\begin{spacing}{\rrxspc}
    However, I argue that this approach offers distinct advantages over traditional Oaxaca-Blinder-Kitagawa decomposition methods. First, by focusing specifically on children from interethnic marriages with similar parental characteristics but different surname ethnicities, I use a more targeted comparison group that better isolates the effect of perceived ethnicity from family background. Traditional decomposition approaches would struggle to separate discrimination effects from the broader socioeconomic gaps between Hispanic and White families overall. Second, the smaller educational and income disparities between HW and WH families compared to HH and WW families, allowing for a clearer attribution of outcome differences to discrimination rather than unobserved heterogeneity. 
\end{spacing}

\begin{spacing}{\rrxspc}
    The empirical evidence supports this approach: Table \ref{tab:synth} shows that interethnic couples are much more similar to each other than endogamous couples are to each other, which is exactly why comparing children of interethnic couples provides a better comparison than comparing children of endogamous marriages. Nevertheless, I acknowledge that residual selection bias remains a concern, particularly regarding cultural and attitudinal factors that may systematically differ between HW and WH households despite similar educational and economic outcomes. Moreover, it is likely that the parenting and cultural backgrounds of interethnic children are more similar to each other than those of children of endogamous marriages.
    \end{spacing}

\begin{spacing}{\rrxspc}
\begin{quotation}
    \textbf{R1: } 2. The analysis sample is restricted to individuals who self-identify as 'White'. It is likely that this self-identification of ethnicity is endogenous to labor market outcomes. Importantly, the unobservable determinants of racial identification are potentially correlated with labor market outcomes. The paper would be improved by including a more thorough discussion of this (sample) selection issue. Related to this is the depiction of parents born in the United States as 'White'. This seems particularly over-simplifying and ignores the long history of immigration. A more accurate description would be to refer to this group as US born.
    \end{quotation}
    \end{spacing}

\begin{spacing}{\rrxspc}
    Thank you for your comments and suggestions. I have addressed both concerns raised by the reviewer. First, regarding the endogeneity of self-identification, I now explicitly discuss this issue in the data section. I explain that ``The sample is restricted to Hispanic and non-Hispanic White individuals to avoid confounding racial factors.'' I argue that including those who do not identify as White could contaminate the estimate of bias against Hispanics due to racial signals. Moreover, as shown by \textcite{hadah2024effect}, there exists strong correlation between bias against Hispanics and self-reported Hispanic identity, and excluding Hispanics who experience ethnic attrition could lead to overestimated bias in the most discriminatory states. To address the comment on the long history of immigration in the US, I updated the manuscript to make clear that the interethnic children I am studying are US born. I also added the following: ``This study's focus on US-born children with foreign-born parents means the findings may not generalize to Hispanic children with US-born parents, who likely face different socioeconomic and cultural circumstances. The analysis does not account for heterogeneity in immigrant characteristics in different Spanish-speaking countries of origin, such as variations in educational attainment, socioeconomic status, and gender-specific migration patterns, which could influence both parental selection in migration and subsequent child outcomes.''
\end{spacing}

\begin{spacing}{\rrxspc}
    Second, regarding the characterization of US-born parents, I have revised the language throughout the manuscript to make it clear that the analysis focuses on US-born individuals. I now explicitly address this concern: ``While the United States has a long history of immigration, the probability that a US-born parent in this sample is a second-generation or later immigrant from a Spanish-speaking country is very low, as shown in Table \ref{tab:mat3}. The majority of Hispanics in the US during this period were first- and second-generation immigrants. Only 3\% of native-born Americans identified as Hispanic during this period, making it statistically unlikely that an interethnic child with a native-born parent is also a second-generation Hispanic immigrant.'' I have also changed terminology throughout to use ``US-born'' rather than ``White'' when referring to native-born parents, and I clarify that this approach ``provides a cleaner identification of surname effects, which is the primary focus of this study.''
\end{spacing}

\begin{spacing}{\rrxspc}
    \begin{quotation}
        \textbf{R1: } 3. The discussion on the construction of the 'synthetic parents' is somewhat brief. The paper suggests that the potential parents are matched using the birth year of the child and the parent's place of birth to the children's information collected in the CPS sample. While not explicitly stated in the paper, I assume that this sample of synthetic parents is used to construct mean parental education and family income at the time of the birth of the child. The process for matching the potential parents to the children is somewhat aggregated and their is likely considerable heterogeneity in the mean educational attainment of the potential parents within the set of children with the same birth year with the same parent's country of birth. The paper could be improved by exploring the possibility of improving the quality of the match of potential parents by including further characteristics to match the potential parents to their children.
\end{quotation}
    \end{spacing}

\begin{spacing}{\rrxspc}
        Thank you for raising this point. I have significantly expanded the discussion of synthetic parents construction and provided a detailed concrete example. In the data section, I now include: ``To illustrate the construction of synthetic parents more concretely, consider someone who was 35 years old in 1999, meaning they were born in 1964. If this person's mother was born in Mexico and their father was born in the United States, their 'synthetic parents' would be identified using the 1970 Census data, when the person was 6 years old. The 'synthetic mother' would have the average characteristics (education, income, etc.) of Mexican-born women who were married to US-born men and had children around 1964, when they were between 20 and 35 years old (meaning they were born between 1929 and 1944). Similarly, the 'synthetic father' would have the average characteristics of US-born men who were married to Mexican-born women and had children in that same year.''

        I acknowledge the reviewer's suggestion about including additional characteristics to improve the matching quality. While incorporating more matching variables (such as parent's age at birth) could potentially reduce heterogeneity within the synthetic parent groups, the current approach balances precision with sample size considerations. Adding more matching criteria would create increasingly small cells in the Census data, potentially leading to unstable estimates or empty cells, particularly for less common parent birthplace combinations. Moreover, since the synthetic parent characteristics serve as controls rather than the primary variables of interest, the current level of aggregation is sufficient for the paper's main empirical strategy. 
\end{spacing}

\begin{spacing}{\rrxspc}
    I also acknowledge the limitations: ``This aggregation process introduces some heterogeneity, as individual parents vary considerably from these group-level measures. However, this approach provides valuable information about typical family background characteristics that would otherwise be completely unobserved. The synthetic parents' characteristics serve as useful proxies for the socioeconomic environment in which these children were raised, allowing me to control for important background factors that influence educational and labor market outcomes. While more refined matching would be ideal, the publicly available data limit the potential matching dimensions. Nevertheless, the current approach provides meaningful estimates while acknowledging these data constraints.''
\end{spacing}

\begin{spacing}{\rrxspc}
    \begin{quotation}
        \textbf{R1: } 4. The description of the estimated model is somewhat brief. However, there are two main issues associated with statistical inference on the estimated parameters in model (1). First, there is a 'generated regressor' issue associated with using estimated group-level parental education. A failure to account for this sampling variation will lead to misleadingly small standard errors. Second, given this group structure for parental education, it seems reasonable to assume that the model errors are uncorrelated across clusters but correlated within (potential parents) clusters. It is well understood that failing to account for this 'clustering' problem can lead to misleadingly small standard errors, narrow confidence intervals, and low p-values.
    \end{quotation}
\end{spacing}

\begin{spacing}{\rrxspc}
    I am grateful to the referee for raising this important concern. I have expanded the discussion of these methodological issues in the empirical approach section. Regarding the generated regressor issue: ``The parental characteristics are included solely as controls and not for inference purposes. I do not interpret these coefficients, as my primary interest lies in $\beta_1$, which captures the gap between Hispanic and White last names. Since I am only using these synthetic characteristics as controls and not making inference about their coefficients, this should not affect the standard errors or p-values of my coefficient of interest $\beta_1$.''

    Regarding the clustering concern: To address this issue, I re-estimated the log annual earnings model using standard errors clustered at the parental birthplace level (mother's and father's birthplace), which corresponds to the level at which `synthetic' parental characteristics were estimated---see table below. The clustered standard errors for $\beta_1$ became slightly smaller (ranging from 0.00 to 0.01 across specifications) compared to the original specification. The fact that standard errors decreased rather than increased after clustering indicates that the original standard errors were, if anything, conservative for my main coefficient of interest. Moreover, since immigrants from Spanish-speaking countries have strong heterogeneous geographical preferences on where to live, clustering at the state level would further address the concern raised by the referee. For example, Cuban immigrants strongly select Florida when they move to the US, while Mexican immigrants self-select to California and Texas. This geographical clustering pattern actually strengthens the case for state-level clustering, as it directly addresses the referee's concern about spatial correlation in the error term. By clustering standard errors at the state level, I account for this within-state correlation that arises from the non-random geographical distribution of immigrant groups.

\newgeometry{bottom=1.0in}
\input{10-JERP-v3/tab0000-regression-cluster}
\restoregeometry

\begin{spacing}{\rrxspc}
\begin{quotation}
    \textbf{R1: } 5. The paper would be improved through an expanded discussion of the impact of measurement error on the reported estimates. While there is a well understood result in the measurement error literature that measures of group mean parental education will provide estimates that are more robust to the presence of measurement error in individual level measures of parental education, there is still an issue with the non-random attrition of potential parents. Specifically, not all potential parents have children in the CPS sample, nor do all children in the CPS sample have parents in the sample of potential parents. Moreover, the non-random attrition of potential parents implies that mean parental education may be systematically higher or lower than the actual parental education of the children in the CPS sample. The paper would be improved by providing an expanded discussion of the likely impacts of measurement error on the reported estimates.
    \end{quotation}
\end{spacing}
\begin{spacing}{\rrxspc}
    Thank you for your comments. I have clarified this methodological point and expanded the discussion of measurement error concerns. First, I want to clarify that the concern about attrition does not apply to my analysis: The synthetic parents are constructed using the birth year of the child and are not based on actual parents in the CPS sample at the time of the survey. The place of birth of parents---mothers and fathers---are questions asked of all participants in the Current Population Survey (CPS) starting 1994. Therefore, I do not use the information of parents who are in the CPS sample at the time of the survey, and I construct synthetic parents from Census data. Because this approach uses Census data rather than contemporaneous parent-child pairs, concerns about non-random attrition of parents from the CPS sample do not apply to my analysis. 
    \end{spacing}

\begin{spacing}{\rrxspc}     
    Regarding measurement error more broadly, I have expanded the discussion in the empirical approach section: ``A potential concern is measurement error in using CPS data to infer parental ethnicity, since it relies on place of birth rather than self-identified Hispanic origin. However, during the period studied, second-generation Hispanics were rare: only about 3\% of native-born Americans identified as Hispanic (see Table \ref{tab:mat3}, which presents Hispanic identification rates by nativity). This makes it unlikely that US-born parents in interethnic unions are second-generation+ Hispanic immigrants.''
    \end{spacing}
\begin{spacing}{\rrxspc}
    Additionally, while using census averages for synthetic parent characteristics does introduce some imprecision compared to actual parent data, this approach avoids the selection bias that would arise from using only parent-child pairs who remain in the CPS sample. The synthetic parents methodology, used by \textcite{rubinstein2014pride}, provides population-level averages that are more representative than the selected sample of parents who happen to be surveyed alongside their children. Moreover, since these synthetic parent controls are not interpreted causally, any measurement error from using group means rather than individual-level data is unlikely to bias the estimated surname effect, which is the key parameter of interest.
    \end{spacing}

@@

\clearpage
\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PART VII. Online Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{refsection}
% Reset section numbering
\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thesubsection}{\Alph{section}.\arabic{subsection}}
\renewcommand{\thesubsubsection}{\Alph{section}.\arabic{subsection}.\arabic{subsubsection}}
\setcounter{page}{1}

### 2025-06-13 manuscripts/10-JERP-v3/tab12-occ.tex
edit manuscript

\begin{table}[H]
\centering\centering
\caption{Descriptive Statistics About Selection Into Occupation by Type \label{tab:occ-sum}}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{}lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{Hispanic Last Name} & \multicolumn{1}{c}{White Last Name} & \multicolumn{2}{c}{Difference-in-means: HW - WH} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-5}
Occupation & Hispanic-White & White-Hispanic & Difference & p value\\
\midrule
\textbf{Management and Business} & 0.111 & 0.129 & -0.018 & 0.000\\
\textbf{STEM Occupations} & 0.030 & 0.040 & -0.009 & 0.000\\
\textbf{Healthcare Occupations} & 0.063 & 0.058 & 0.005 & 0.002\\
\textbf{Education and Social Services} & 0.062 & 0.064 & -0.002 & 0.237\\
\textbf{Arts, Media, and Entertainment} & 0.028 & 0.034 & -0.006 & 0.000\\
\addlinespace
\textbf{Service Occupations} & 0.107 & 0.099 & 0.008 & 0.000\\
\textbf{Manual and Industrial Labor} & 0.199 & 0.171 & 0.028 & 0.000\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: Current Population Survey (CPS) 1994-2019.
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\begin{table}[H]
\centering\centering
\caption{Descriptive Statistics About Selection Into Occupation by Type \label{tab:occ-sum}}
\centering
\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
\begin{threeparttable}
\begin{tabular}[t]{>{}lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{Hispanic Last Name} & \multicolumn{1}{c}{White Last Name} & \multicolumn{2}{c}{Difference-in-means: WH - HW} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-5}
Occupation & Hispanic-White & White-Hispanic & Difference & p value\\
\midrule
\textbf{Management and Business} & 0.111 & 0.129 & -0.018 & 0.000\\
\textbf{STEM Occupations} & 0.030 & 0.040 & -0.009 & 0.000\\
\textbf{Healthcare Occupations} & 0.063 & 0.058 & 0.005 & 0.002\\
\textbf{Education and Social Services} & 0.062 & 0.064 & -0.002 & 0.237\\
\textbf{Arts, Media, and Entertainment} & 0.028 & 0.034 & -0.006 & 0.000\\
\addlinespace
\textbf{Service Occupations} & 0.107 & 0.099 & 0.008 & 0.000\\
\textbf{Manual and Industrial Labor} & 0.199 & 0.171 & 0.028 & 0.000\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[1] Source: Current Population Survey (CPS) 1994-2019.
\end{tablenotes}
\end{threeparttable}}
\end{table}
